### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

\subsection{Sprint 4: Build and Publish}

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{Figures/thumb.png}
\caption{The Icon Used for Publication}
\end{figure}

@@

\subsection{Sprint 2: Project Planning}

@@

\section{Conclusion}

>>>>

\subsection{Sprint 4: Build and Publish}
This sprint was focused on having the artefact being available standalone without the need of the editor.
\\\\
The Unity Editor has a function to export the game as a standalone application without the need of the editor. The settings for this range from they level of detail to be kept from the original assets, such as the models, and the quality of lighting. The overall quality setting of "High" was chosen as it allows for a balance between visual quality and performance. Performance in this regard refers to how well the application ran on a system without a dedicated graphics card unit. Additionally, an icon for the executable file could be set here.
\\\\
Once the build settings had been finalised the artefact was exported from the Unity Editor as a standalone application. During this process, unforeseen complications arose. The main issue here was that certain references between certain scripts were returning null values. These references functioned as intended while within the editor which caused initial confusion. As a result from this, certain scripts were slightly reworked so that the necessary references would work again. 
\\\\
Once the above complication was dealt with, the game was published on itch.io, a video game hosting website, where it is available for download\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}}. Figure \ref{thumb} is the icon used as the icon that is displayed on the website.

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{Figures/thumb.png}
\caption{The Icon Used for Publication}
\label{thumb}
\end{figure}

@@

\subsection{Sprint 2: Project Planning}
This phase of the project included the development of a provisional project plan which included discussions around which paradigm the research would be classified under. The interpretivistic paradigm was chosen for the fact that it caters for research which needs to be done through multiple viewpoints, fields or lenses. During this phase, the fields that were to be researched were finalised. These being pedagogy, ludology and gamification. It was also decided during this phase that case studies would be used as well. The aims and objectives set out during the previous phase were also refined.
\\\\
This phase was completed upon the submission of the planning document.

@@

\section{Conclusion}
This section detailed the developmental processes and phases of both the artefact and article that form a part of this project as well as the issues faced at certain points. For both, an adapted Agile methodology closer to the Scrum methodology was used with the article blending that with design science.
